\chapter*{ABSTRACT}
\addcontentsline{toc}{chapter}{ABSTRACT}

\textit{In the midst of rapid developments in the digital age, access to scientific exegesis literature on the Qur'an is still limited, especially in an easily accessible and systematically organised digital format. However, scientific exegesis plays an important role in linking the verses of the Qur'an with scientific phenomena, thereby strengthening the integration between science and religious teachings. This research aims to develop a scientific exegesis website for the Qur'an that presents a collection of science-themed verses along with their exegesis, translations, and supporting references in a systematic manner. The development was carried out using the Model-View-Controller (MVC) architecture based on the Laravel framework, chosen for its ability to separate logic, presentation, and data, thereby facilitating system management and maintenance. The development method follows the waterfall model through the stages of requirements analysis, design, implementation, and testing. Testing includes expert validation by media experts, subject matter experts, user testing, and black-box testing to ensure all functions operate according to specifications. The test results showed a high level of feasibility, with scores of 86.20\% from media experts, 87\% from material experts, and 86.14\% from users, while black-box testing proved that all features functioned properly. With these achievements, the website is considered feasible for use as a digital learning medium that supports the integration of science and religion. Recommendations for further development could focus on adding semantic search features and integrating interactive multimedia content to enhance the user experience.}\\	%edited

\noindent\textit{\textbf{Keywords:} science exegesis, integration of religion and science, laravel, model-view-controller (mvc), digitalization.}\\	%edited


