\chapter*{ACKNOWLEDGEMENTS}
\addcontentsline{toc}{chapter}{ACKNOWLEDGEMENTS}

Praise and gratitude to the presence of Allah SWT who has given His blessings and guidance so that the thesis entitled "THESIS IMPLEMENTATION USING LATEX" can be completed. This thesis is one of the requirements to complete the study and obtain a Bachelor of Computer Science degree in the Informatics Engineering Study Program, Darussalam Gontor University. The series of works on this thesis would not have been able to be completed until now without the help of various parties. Therefore, the author would like to express his gratitude for the help and support that has been given to:	%edited

\begin{enumerate}
	\item Al-Ustadz Prof. Dr. Hamid Fahmy Zarkasyi, M.A.Ed., M.Phil., as the Chancellor of Darussalam Gontor University and all his staff, as well as all the lecturers of Darussalam Gontor University Ponorogo who have educated the author.
	\item Al-Ustadz Dr. Haris Setyaningrum, M.Sc. as Dean of the Faculty of Science and Technology and his staff.
	\item Al-Ustadz Dihin Muriyatmoko, M.T. as Head of the Informatics Engineering Study Program, Darussalam Gontor University.
	%edited
\end{enumerate}

The author realizes that this thesis is far from perfect due to limited experience. Therefore, the author welcomes constructive criticism and suggestions to improve this thesis. Finally, the author hopes that this paper can serve as a reference and resource for those who need it. 	%edited

\begin{flushright}
	\begin{minipage}{5cm} 
		Ponorogo, 8 Agustus 2027	%edited
		\vspace{3cm}\\
		\centering\textbf{\underline{Muhammad Dafi Al Haq}}\\	%edited
		\centering NIM: 452024611067\\	%edited
	\end{minipage}
\end{flushright}